%% MASS/SMASH paper — reframed as general signal-processing methods paper
%% Target: IEEE Transactions on Signal Processing / Signal Processing (Elsevier)
%% Solar wind is a case study, not the primary framing.

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}

\geometry{margin=1in}
\doublespacing

\newcommand{\Bvec}{\mathbf{B}}
\newcommand{\dBvec}{\Delta\mathbf{B}}
\newcommand{\Bhat}{\hat{\mathbf{B}}}
\newcommand{\nT}{\,\mathrm{nT}}
\newcommand{\s}{\,\mathrm{s}}
\newcommand{\MDL}{\mathrm{MDL}}
\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\PVI}{\mathrm{PVI}}
\newcommand{\FDF}{\mathrm{FDF}}
\newcommand{\dBmag}{\left|d|\mathbf{B}|/dt\right|}

\title{\textbf{MASS/SMASH: MDL-Regularized Antipodal Change-Point Detection \\
for Sign-Flip Events in Noisy Time Series, \\
with Application to Solar Wind Current Sheets}}

\author{
  Mac Mayo\\
  \small{SeamAware Research, independent}\\
  \small{\texttt{macmarlins@gmail.com}}
}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Many physical and engineered systems produce time series that undergo
\emph{sign-flip change-points}: transitions from a positive steady state to an
approximately equal-magnitude negative state, embedded in broadband noise.
Existing change-point detection frameworks --- CUSUM, PELT, binary segmentation,
and Bayesian online methods --- detect shifts in mean or variance but do not
exploit the antisymmetric (antipodal) structure specific to sign reversals.
We introduce MASS/SMASH (Multi-seAm Seam-Sensitive Modeling / Symmetric
Minimum-description-length Antipodal Seam Hunting), the first change-point
detector to combine: (1) an antipodal correlation scanner that scores positions
where $y(t) \approx -y(t+\Delta t)$, (2) a roughness discontinuity detector
that identifies abrupt changes in local signal variance, and (3) a Minimum
Description Length (MDL) model-selection step that accepts a detection only when
the two-segment compression gain exceeds the $\approx \log_2 N$-bit cost of
recording the seam location.

We demonstrate MASS/SMASH on a well-studied case from space physics: detecting
magnetic polarity reversals (current sheets) in solar wind time series.
Against 120 known injected polarity reversals in 30 days of synthetic solar wind
data (3-s cadence, 30\% Kolmogorov turbulence, signal-to-noise ratio
$\sim$3:1), MASS/SMASH achieves precision 0.921 (false discovery fraction 7.9\%)
and recall 0.483 (F1 = 0.634).
The competing partial-variance-of-increments (PVI) detector achieves
precision 0.989 / recall 0.750 (F1 = 0.853), while a $d|\mathbf{B}|/dt$
threshold baseline achieves precision 0.909 / recall 1.000 (F1 = 0.952).
MASS/SMASH is the most conservative selector, producing 63 detections with
5 false positives; it captures 24 crossings missed by PVI, and a joint
MASS/SMASH $+$ PVI catalog recovers 95\% of injected events with a
$\sim$5\% combined false discovery fraction.

We further identify and diagnose a systematic $\pm 30\,\mathrm{s}$ localization
offset in MASS/SMASH detections, which arises from finite chunked-inference
discretization and the forward-ordered antipodal correlation formula.
When rotation angles are computed at matched ground-truth positions, MASS/SMASH
true-positive events are statistically indistinguishable from the PVI catalog,
establishing that the MDL criterion selects genuine polarity reversals rather than
a physically distinct sub-population.
We discuss extensions to magnetospheric physics, EEG, climate regime shifts, and
power systems fault detection.
\end{abstract}

\textbf{Keywords:} change-point detection; sign-flip; antipodal correlation;
Minimum Description Length; solar wind; current sheets; partial variance of
increments; structural break; information theory

\clearpage

%% ============================================================
\section{Introduction}
\label{sec:intro}
%% ============================================================

\subsection{The Sign-Flip Change-Point Problem}

Consider a time series $y(t)$ drawn from a stationary process with mean
$+\mu_0$ that, at an unknown time $t^*$, undergoes an abrupt or smoothly-transitioning
reversal to mean $-\mu_0$.
This \emph{sign-flip change-point} --- a polarity reversal embedded in
broadband noise --- recurs across a wide range of physical and engineered systems.
In geospace physics, magnetic field polarity reversals occur at heliospheric
sector boundaries in the solar wind, at current sheet crossings in the
magnetospheric tail, and at flux rope boundaries throughout the heliosphere
\citep{Greco2008,Chasapis2015}.
In biomedical signal processing, re-referencing or phase-inversion artifacts
in electroencephalography (EEG) produce sign flips in individual channels,
and certain seizure morphologies transition between positive and negative
slow-wave polarity \citep{Shoeb2004}.
In climate science, major climate modes --- the El Niño--Southern Oscillation
(ENSO), the Atlantic Multidecadal Oscillation (AMO), the Pacific Decadal
Oscillation --- reverse polarity on interannual to interdecadal timescales,
with the transition embedded in internal variability noise \citep{Trenberth1990}.
In power systems, line-to-line faults and inverter failure modes produce
characteristic sign-flip patterns in current and voltage waveforms that must be
detected within milliseconds.

What unites these problems is a shared statistical structure: \emph{the signal
on opposite sides of the transition is approximately the negative of the signal
on the same side}.
This antisymmetric --- or antipodal --- structure is a stronger constraint than
a generic mean-shift, and it is exploitable.
Yet the classical literature on change-point detection has not, to our knowledge,
developed a framework that explicitly targets sign-flip events by scoring
candidate positions for antisymmetry rather than for raw gradient magnitude.

\subsection{Limitations of Existing Change-Point Methods}

Classical change-point detection methods are well-developed for mean-shift,
variance-shift, and distributional-shift events.
The CUSUM (cumulative sum) statistic \citep{Page1954} detects persistent mean
offsets with high power under sequential testing, but it is directional:
detecting a reversal requires running two sequential CUSUMs in opposite directions.
Binary segmentation \citep{Vostrikova1981} recursively splits the series at the
single most significant change-point, offering simplicity but suboptimal
performance for multiple nearby events.
The PELT algorithm \citep{Killick2012} solves the penalized segmentation problem
$\min_m \sum_{i=1}^{m+1} C(y_{t_{i-1}+1:t_i}) + \beta m$ in $\mathcal{O}(n)$
time using dynamic programming with a pruning step, but the cost function $C$
targets mean/variance fit quality, not antisymmetric structure.
Bayesian online change-point detection \citep{AdamsMacKay2007} maintains a
posterior over run-length since the last change, providing principled uncertainty
quantification, but again relies on standard predictive likelihood, not an
antipodal candidate score.
MDL-based change-point methods \citep{Rissanen1978,Davis2006} use the description
length of the piecewise model as a complexity-penalized objective; these are the
closest precursors to MASS/SMASH but do not include an antisymmetry candidate
filter.

All of these methods share a structural limitation for sign-flip detection: they
treat the pre-transition and post-transition signals as \emph{independently}
distributed segments.
They cannot cheaply score whether the two segments are antipodal, because their
cost functions are defined per-segment, not across the boundary.
For sign-flip problems, a filter that first tests for antisymmetry --- and passes
only those positions that score well --- would reduce the candidate pool to
a manageable set and make the MDL scoring more efficient and more targeted.

\subsection{MASS/SMASH: Antipodal Candidates + MDL Acceptance}

We introduce MASS/SMASH (Multi-seAm Seam-Sensitive Modeling / Symmetric
Minimum-description-length Antipodal Seam Hunting), which combines:
\begin{enumerate}
  \item An \textbf{antipodal correlation detector} that scores each time
    index for antisymmetry between the forward and backward half-windows
    (Section~\ref{subsec:antipodal}).
  \item A \textbf{roughness discontinuity detector} that scores for abrupt
    changes in local signal variance, complementing the antipodal score for
    events with turbulent or asymmetric transition profiles
    (Section~\ref{subsec:roughness}).
  \item An \textbf{MDL model-selection step} that accepts a proposed seam only
    when the description-length reduction from a two-segment piecewise model
    exceeds the $\approx \log_2 N$-bit cost of specifying the seam location
    (Section~\ref{subsec:mdl}).
\end{enumerate}

The antipodal score filters the candidate pool to positions structurally
consistent with sign flips; the MDL step then asks whether the improvement in
data compression is statistically worth the model complexity cost.
This two-stage filter-and-select design provides conservative detection:
events are retained only when they simultaneously match the expected antipodal
structure \emph{and} demonstrate statistically significant compressibility gain.

To our knowledge, MASS/SMASH is the first change-point detection framework to
combine an antipodal (sign-flip) symmetry score as the primary candidate
generator with an MDL regularized acceptance criterion.

\subsection{Solar Wind as a Case Study}

We validate MASS/SMASH on a well-characterized instance of the sign-flip
detection problem: detecting magnetic polarity reversals (current sheets) in
turbulent solar wind time series.
This domain is well-suited as a benchmark for several reasons.

First, the signal structure matches the sign-flip template: across a current
sheet crossing the magnetic field component normal to the sector boundary
(typically the heliocentric radial or $B_z$ component) transitions from
$+B_0$ to $-B_0$, with the transition embedded in Kolmogorov-spectrum
turbulence at 20--40\% amplitude.

Second, a high-performance comparison detector exists: the Partial Variance
of Increments \citep[PVI;][]{Greco2008} is a well-validated, gradient-based
detector for coherent structures in solar wind turbulence, providing a strong
non-trivial baseline for precision-recall comparison.

Third, synthetic ground truth is straightforward to generate: we inject known
polarity reversals and recover their exact centers deterministically, enabling
rigorous evaluation that is impossible on real-world data without labeled catalogs.

The solar wind case study does not exhaust the scope of MASS/SMASH; we discuss
extension to magnetospheric physics, EEG, climate, and power systems in
Section~\ref{sec:applications}.

\subsection{Organization}

Section~\ref{sec:related} reviews related change-point detection work.
Section~\ref{sec:algorithm} describes the MASS/SMASH algorithm.
Section~\ref{sec:casestudy} describes the solar wind case study: synthetic data,
comparison detectors, and evaluation protocol.
Section~\ref{sec:results} presents detection performance and the rotation angle
localization analysis.
Section~\ref{sec:discussion} interprets the results, discusses complementarity
with PVI, and characterizes limitations.
Section~\ref{sec:applications} describes broader applicability and extensions.
Section~\ref{sec:conclusions} summarizes the main contributions.

%% ============================================================
\section{Related Work}
\label{sec:related}
%% ============================================================

\subsection{Change-Point Detection}

The change-point detection literature has developed largely around three problem
classes: (1) detecting a single change-point in a sequence of independent
observations \citep{Page1954,Hinkley1970}, (2) detecting multiple change-points
in an offline setting \citep{Vostrikova1981,Lavielle2005,Killick2012}, and
(3) online detection of a change as data arrive sequentially
\citep{AdamsMacKay2007,Fearnhead2007}.
Comprehensive reviews are provided by \citet{Basseville1993} and \citet{Truong2020}.

PELT \citep{Killick2012} is the current state-of-the-art offline algorithm for
multiple change-points under a sum-of-segment-costs objective with a linear penalty
on the number of change-points.
Its cost function supports Gaussian mean shifts, variance shifts, and arbitrary
distributional changes via maximum likelihood; extensions to non-parametric costs
have been developed in the \texttt{ruptures} library \citep{Truong2020}.
Bayesian online change-point detection \citep{AdamsMacKay2007} maintains an
exact posterior over run-length and provides calibrated uncertainty estimates;
its main computational cost is $\mathcal{O}(n^2)$ per step in the naive
implementation.

MDL-based segmentation \citep{Rissanen1978,Davis2006} treats change-point
detection as piecewise model selection: the number and locations of
change-points are chosen to minimize the total description length of the
model plus the data given the model.
This formulation naturally handles unknown model order within each segment and
penalizes over-segmentation through the $\log_2 N$-bit location cost.
MASS/SMASH uses an MDL criterion with a richer per-segment model zoo (Fourier,
polynomial, and autoregressive alternatives) than is standard in the
change-point literature.

\subsection{Sign-Flip and Antisymmetric Change-Points}

Standard change-point methods do not distinguish between a mean shift from
$+\mu$ to $+2\mu$ and one from $+\mu$ to $-\mu$.
Both are detected by the same CUSUM or PELT cost; neither method scores whether
the pre-transition and post-transition signals are antisymmetric.
For datasets where the change is specifically a polarity reversal (amplitude
preserved, sign inverted), the antisymmetric structure constitutes a strong
additional constraint that, if exploited, should improve precision by filtering
out generic gradient events.

We are not aware of prior work that uses a correlation-based antisymmetry score
as the primary candidate generator for change-point detection, though boundary
detection in image processing sometimes uses mirrored filter responses
\citep{Canny1986}.

\subsection{Solar Wind Current Sheet Detection}

In heliophysics, automated current sheet detection relies primarily on:
(1) the Partial Variance of Increments \citep{Greco2008,Greco2009}, which
thresholds the normalized lagged increment $|{\dBvec(t,\tau)}| /
\sqrt{\langle|\dBvec|^2\rangle_T}$;
(2) directional discontinuity analysis based on minimum variance or hodogram
criteria \citep{Neugebauer1984};
(3) wavelet decomposition for intermittency characterization \citep{Bruno2013}.
None of these methods combines an antisymmetry candidate score with
MDL-regularized model selection.
MASS/SMASH is presented as a complementary selector, not a replacement for
well-calibrated gradient detectors such as PVI.

%% ============================================================
\section{The MASS/SMASH Algorithm}
\label{sec:algorithm}
%% ============================================================

MASS/SMASH processes a univariate time series $y_1, \ldots, y_N$ and returns
a set of seam locations $\{\tau_1, \ldots, \tau_m\}$ with associated MDL
gain scores.
The pipeline has four stages: (1) candidate proposal from two detectors,
(2) non-maximum suppression (NMS), (3) per-configuration MDL scoring, and
(4) global MDL selection.
Although we describe the algorithm in the solar wind context for concreteness,
all components are domain-agnostic; the only domain-specific choice is which
signal component to process.

\subsection{Antipodal Correlation Detector}
\label{subsec:antipodal}

The antipodal correlation detector scores each candidate position $\tau$ by:
\begin{equation}
  \mathcal{A}(\tau) \;=\; \mathrm{corr}\!\left(y[\tau-w:\tau],\;
    -\,y[\tau:\tau+w]\right),
  \label{eq:antipodal}
\end{equation}
where $w$ is the half-window size (default 20 samples) and both windows are
$z$-score normalized before computing the Pearson correlation.
The score $\mathcal{A}(\tau) \approx 1$ when the $w$ samples immediately before
$\tau$ have the same temporal pattern as the $w$ samples immediately after $\tau$,
but with reversed sign --- the defining signature of a polarity reversal.

A note on the formula: equation~\eqref{eq:antipodal} compares the
\emph{forward-ordered} pre-window $y[\tau-w:\tau]$ with the
\emph{forward-ordered} negated post-window $-y[\tau:\tau+w]$.
This is not identical to true \emph{mirror} antisymmetry, which would require
one window to be reversed before correlation:
$\mathrm{corr}(y[\tau-w:\tau],\,-\,\mathrm{reverse}(y[\tau:\tau+w]))$.
For a sharp sign flip where both windows are approximately uniform --- one at
$+\mu_0$, one at $-\mu_0$ after negation --- both formulas agree to good
approximation.
For wider or asymmetric transitions, they differ.
We characterize the empirical localization behavior in
Section~\ref{subsec:offset} rather than making analytic claims about which
profile feature the detector locates precisely.
Candidates are local maxima of $\mathcal{A}$ above a threshold
(default 0.35), retained after NMS with minimum separation 60 s.

\subsection{Roughness Discontinuity Detector}
\label{subsec:roughness}

The roughness at position $i$ is $\mathcal{R}(i) = \sigma(\Delta y[i:i+w_r])$,
where $\Delta y$ denotes first differences and $w_r$ is the roughness window
(default 20 samples).
The detector score is the normalized roughness change:
\begin{equation}
  \mathcal{D}(\tau) \;=\;
    \frac{|\mathcal{R}(\tau) - \mathcal{R}(\tau-1)|}{\sigma(\mathcal{R})}.
  \label{eq:roughness}
\end{equation}
Candidates are local maxima of $\mathcal{D}$ above threshold 0.20, again with
NMS.
The roughness detector is complementary to the antipodal scanner: it fires where
the local variance structure changes, which includes the edges of a transition
layer even when the antipodal symmetry is diluted by high-amplitude noise.
Together, the two detectors cover both clean reversals (antipodal detector
dominant) and embedded reversals in turbulent intervals (roughness detector
supplements).

\subsection{MDL Model Selection}
\label{subsec:mdl}

After merging the top-$k^*$ candidates from both detectors (default $k^*=3$
per detector), MASS/SMASH scores all seam configurations (subsets of at most
$m_\mathrm{max}$ candidates) with the MDL objective in bits:
\begin{equation}
  \MDL(m, \hat{\boldsymbol{\theta}}) \;=\;
    \underbrace{\frac{N}{2}\log_2\frac{\RSS}{N}}_{\text{data fit}}
    \;+\;
    \underbrace{\frac{p}{2}\log_2 N}_{\text{model complexity}}
    \;+\;
    \underbrace{\frac{\alpha}{2}\,m\,\log_2 N}_{\text{seam encoding}},
  \label{eq:mdl}
\end{equation}
where $\RSS$ is the pooled residual sum of squares across segments, $p$ is the
total model parameter count, $m$ is the number of seams, and $\alpha = 2.0$
is the seam penalty coefficient.
The seam encoding term reflects the information cost of recording $m$ seam
positions from $N$ possible locations ($\approx m\log_2 N$ bits).
This term enforces the core principle: each seam must compress the data by more
than the cost of specifying its location in the description.

Within each segment, MASS/SMASH evaluates a model zoo: Fourier series at
three complexity levels ($K = 4, 8, 12$ harmonics), polynomials of degree
2, 3, and 5, and autoregressive models of orders 5, 10, and 15.
The best model per segment is selected by its BIC contribution; the pooled
$\RSS$ and $p$ enter equation~\eqref{eq:mdl}.
The configuration minimizing total MDL is returned; a no-seam configuration
($m=0$) is always included as a baseline, so a detection requires an explicit
positive MDL improvement over the single-segment model.

\subsection{Chunked Inference on Long Time Series}
\label{subsec:chunked}

For long time series, MASS/SMASH applies in a sliding-window fashion:
windows of length $W$ samples at step $S < W$ samples.
Each window is processed independently with $m_\mathrm{max}=1$.
Each sample accumulates a cumulative MDL gain across all windows in which it
was selected as a seam.
A global NMS pass retains peaks above a gain threshold $G$ with minimum
inter-event separation.

For the solar wind case study ($N = 864{,}000$ samples), we use $W = 200$
samples (600 s), $S = 100$ samples (300 s), yielding 8{,}638 overlapping chunks.
The gain threshold $G = 20$ bits for the main benchmark and $G = 2$ bits for
exploratory analysis.
Algorithm~\ref{alg:chunked} summarizes the full pipeline.

\begin{algorithm}[t]
\caption{MASS/SMASH chunked inference}
\label{alg:chunked}
\begin{algorithmic}[1]
\Require Signal $y[0:N]$, window $W$, step $S$, gain threshold $G$
\State Initialize $\mathrm{gain}[0:N] \gets 0$
\For{$\mathrm{start} \in \{0, S, 2S, \ldots, N-W\}$}
  \State Run MASS/SMASH on $y[\mathrm{start}:\mathrm{start}+W]$ with $m_\mathrm{max}=1$
  \If{best solution has $m>0$ and MDL gain $g>0$}
    \For{each local seam index $\tau_\ell$}
      \State $\mathrm{gain}[\mathrm{start}+\tau_\ell] \mathrel{+}= g$
    \EndFor
  \EndIf
\EndFor
\State Retain positions with $\mathrm{gain} > G$; NMS with $\Delta\tau_\mathrm{min}$
\State \Return detected positions and scores
\end{algorithmic}
\end{algorithm}

%% ============================================================
\section{Case Study: Solar Wind Current Sheet Detection}
\label{sec:casestudy}
%% ============================================================

\subsection{Synthetic Solar Wind Data}
\label{subsec:synth}

We validate MASS/SMASH on a 30-day, 3-s-cadence synthetic magnetic field time
series ($N = 864{,}000$ samples) calibrated to mimic Wind/MFI observations
during the March 2001 interval studied by \citet{Osman2014}.

The background field follows a sector-boundary model.
The nominal field direction is
$\hat{\mathbf{b}}_0 = (0.201, 0.201, 0.958)$ (after normalization), giving a
field strength of $B_0 = 6\nT$ and placing $\approx 96\%$ of the polarity
reversal amplitude in the $B_z$ component.
This geometry is deliberately favorable for single-component detection;
we discuss implications in Section~\ref{subsec:limits}.
One hundred and twenty synthetic sector-boundary-like polarity reversals are
placed at Poisson-random times with mean rate $\sim$4 per day and minimum
spacing of one hour.
We use the term ``polarity reversal'' deliberately to avoid conflating these
synthetic injections with the large-scale heliospheric current sheet (HCS),
which typically crosses at $\sim$1--2 per solar rotation; the synthetic rate
is consistent with smaller-scale flux-tube boundary crossings observed near
1 AU during moderately active intervals \citep{Wilcox1965}.
At each crossing the polarity transitions via:
\begin{equation}
  \mathrm{pol}(t) \;=\; \tanh\!\left(\frac{t - t_\mathrm{cross}}{\delta/3}\right)
  \label{eq:tanh}
\end{equation}
with transition widths $\delta$ drawn uniformly from $[15\s, 60\s]$, comparable
to observed current sheet thicknesses at 1 AU \citep{Vasquez2007}.

Turbulence is superimposed with power spectral density $P(f) \propto |f|^{-5/3}$
(Kolmogorov spectrum), amplitude $\sigma_\mathrm{turb} = 0.30 B_0 = 1.8\nT$ per
component, consistent with typical amplitude ratios $\delta B/B \sim 0.2$--$0.4$
in the inertial range at 1 AU \citep{Bruno2013}.
The resulting field has $|\mathbf{B}|_\mathrm{rms} = 6.5\nT$,
$\sigma_{|\mathbf{B}|} = 1.6\nT$, and $\sigma_{B_z} = 6.0\nT$.

The 120 injected crossing centers are recorded at the exact tanh midpoints
(where $\mathrm{pol}(t) = 0$) and serve as the primary ground truth in all
performance evaluations.
These are recovered deterministically by re-running the generator with the same
random seed; the true crossing positions are exact, not estimated.

\subsection{Comparison Detectors}
\label{subsec:comparators}

\textbf{PVI detector.}
The Partial Variance of Increments \citep{Greco2008}:
\begin{equation}
  \PVI(t) \;=\; \frac{|\dBvec(t,\tau)|}{\sqrt{\langle |\dBvec|^2 \rangle_T}},
  \label{eq:pvi}
\end{equation}
where $\dBvec(t,\tau) = \Bvec(t+\tau) - \Bvec(t)$ is the lagged increment and
the denominator is a running-window variance normalization.
PVI is computed from the full 3-component field with lag $\tau = 1$ sample (3 s)
and a 90-s normalization window.
Crossings are identified as peaks with $\PVI > 3.0$ and minimum inter-event
separation of 300 s, yielding 91 detections for the 30-day interval.
PVI represents the state-of-the-art domain method; it is simultaneously a
detection algorithm (evaluated against injected crossings) and a secondary
reference.
The 91 PVI events are not used as primary ground truth.

\textbf{$d|\mathbf{B}|/dt$ threshold baseline.}
The baseline applies a threshold of $\mu + 2.5\sigma$ to the time derivative
of the scalar field magnitude:
\begin{equation}
  \mathrm{score}(t) \;=\; \left|\frac{d\,|\mathbf{B}|}{dt}\right|,
  \label{eq:baseline}
\end{equation}
with minimum inter-event separation of 300 s.
We note that this statistic is physically distinct from the vector gradient
$|d\mathbf{B}/dt|$: a polarity reversal can rotate $\mathbf{B}$ by $\approx
180^\circ$ while leaving $|\mathbf{B}|$ nearly constant, so $d|\mathbf{B}|/dt$
may not fire strongly at a clean sector-boundary crossing.
We retain this detector as the simplest operational screener and acknowledge
that a vector-gradient or vector-PVI baseline would provide a stronger comparator;
that comparison is left for future work.

\subsection{Evaluation Metrics}
\label{subsec:metrics}

A detected event at position $\hat{\tau}$ is a true positive (TP) if it falls
within a tolerance window of a known injected crossing center; each crossing
is matched at most once.
We report precision $P = \mathrm{TP}/(\mathrm{TP}+\mathrm{FP})$,
recall $R = \mathrm{TP}/(\mathrm{TP}+\mathrm{FN})$, F1, and the
false discovery fraction $\FDF = 1 - P$.
Two tolerance levels are used: 150 s (50 samples) to accommodate the geometric
offset between the detection and the sign-flip center (Section~\ref{subsec:offset}),
and 30 s (10 samples) as a strict reference.

\subsection{Rotation Angle Analysis}
\label{subsec:rotation_method}

For each detection at sample index $p$, the magnetic field rotation angle is:
\begin{align}
  \Bhat_\mathrm{before} &=
    \frac{\langle\Bvec\rangle_{[p-w_a:p]}}{|\langle\Bvec\rangle_{[p-w_a:p]}|}, \quad
  \Bhat_\mathrm{after} \;=\;
    \frac{\langle\Bvec\rangle_{[p:p+w_a]}}{|\langle\Bvec\rangle_{[p:p+w_a]}|},
  \label{eq:Bhat} \\
  \omega &= \arccos\!\left(\mathrm{clip}(\Bhat_\mathrm{before}
    \cdot \Bhat_\mathrm{after}, -1, 1)\right),
  \label{eq:omega}
\end{align}
with averaging windows $w_a \in \{10, 30, 60, 120\}\s$.
We compute $\omega$ both at the raw detection position $p$ and, for matched
true positives, at the corresponding injected crossing center, in order to
separate localization effects from physical differences between detector
populations.

Statistical comparison uses a two-sample Kolmogorov-Smirnov (KS) test.
Phase-randomized surrogates (100 realizations; independent Fourier phase
randomization per component) provide a null model for testing whether
distributional differences are explainable by spectral properties alone.
Because only 100 surrogates are computed, the minimum reportable surrogate
$p$-value is $p < 0.01$.

%% ============================================================
\section{Results}
\label{sec:results}
%% ============================================================

\subsection{Detection Performance Against Injected Crossings}
\label{subsec:detection}

Table~\ref{tab:main_results} summarizes performance for all three detectors
against the 120 injected crossing centers.

\begin{table}[t]
\centering
\caption{Detection performance against 120 known injected crossing centers.
FDF = false discovery fraction = $1 - P$.}
\label{tab:main_results}
\begin{tabular}{lcccccccc}
\toprule
Detector & Tol. & $N_\mathrm{det}$ & TP & FP & $P$ & $R$ & F1 & FDF \\
\midrule
MASS/SMASH (MDL gain $> 20$ bits) & 150 s & 63  & 58 & 5  & 0.921 & 0.483 & 0.634 & 7.9\% \\
MASS/SMASH (MDL gain $> 20$ bits) & 30 s  & 63  & 18 & 45 & 0.286 & 0.150 & 0.197 & 71.4\% \\
\midrule
PVI ($\PVI > 3.0$)                & 150 s & 91  & 90 & 1  & 0.989 & 0.750 & 0.853 & 1.1\%  \\
PVI ($\PVI > 3.0$)                & 30 s  & 91  & 90 & 1  & 0.989 & 0.750 & 0.853 & 1.1\%  \\
\midrule
$d|\mathbf{B}|/dt$ baseline       & 150 s & 132 & 120 & 12 & 0.909 & 1.000 & 0.952 & 9.1\% \\
$d|\mathbf{B}|/dt$ baseline       & 30 s  & 132 & 120 & 12 & 0.909 & 1.000 & 0.952 & 9.1\% \\
\bottomrule
\end{tabular}
\end{table}

Several findings are evident from Table~\ref{tab:main_results}.

\textbf{The $d|\mathbf{B}|/dt$ baseline achieves perfect recall.}
All 120 injected crossings are matched within 150 s; the 12 false detections
correspond to high-gradient turbulent fluctuations that did not originate from
injected crossings.
Because the baseline and the tanh crossings are both gradient-based, performance
is identical at the 30-s and 150-s tolerance levels.

\textbf{PVI achieves the highest precision but misses 25\% of injected crossings.}
PVI finds 90 of 120 injected crossings with only 1 spurious detection (FDF =
1.1\%).
The 30 missed crossings are weak events --- those with smaller $B_z$ amplitude
at the crossing center due to overlapping turbulent fluctuations --- that do not
exceed the $\PVI > 3.0$ threshold.
PVI performance is identical at both tolerance levels because PVI peaks at the
gradient maximum of the tanh transition, which coincides with the midpoint.

\textbf{MASS/SMASH is the most conservative selector, with comparable precision
to PVI and the baseline.}
Of 63 MASS/SMASH detections, 58 (92.1\%) are within 150 s of an injected
crossing.
MASS/SMASH recall (0.483) is substantially lower than the baseline (1.000) or
PVI (0.750), reflecting the conservative MDL gain threshold (20 bits).
At strict 30-s tolerance, MASS/SMASH recall falls to 0.150, indicating that
most detections are offset from the crossing center by more than 30 s;
Section~\ref{subsec:offset} explains this offset.

\textbf{MASS/SMASH finds crossings that PVI misses.}
Of the 58 MASS/SMASH true-positive detections, 24 correspond to crossings not
in the PVI catalog.
A joint MASS/SMASH $+$ PVI catalog would cover $90 + 24 = 114$ of 120 injected
crossings (95\%) with a combined false discovery fraction of approximately 5\%
(6 false positives out of $\sim$120 combined unique detections).

\subsection{Detection Localization: A Systematic Offset from the Polarity Center}
\label{subsec:offset}

The drop from 0.483 recall at 150-s tolerance to 0.150 at 30-s tolerance reveals
that most MASS/SMASH true positives are offset from the injected crossing center
by 30--150 s.
For each true positive MASS/SMASH detection, we compute the displacement from
the matched injected crossing center:
\begin{equation}
  \Delta\tau_i = \tau_i^\mathrm{MS} - \tau_i^\mathrm{inj},
\end{equation}
where $\tau_i^\mathrm{MS}$ is the MASS/SMASH detection position and
$\tau_i^\mathrm{inj}$ is the nearest injected crossing center within 150 s.

The offset distribution clusters near $\Delta\tau \approx \pm 10$
samples ($\pm 30\s$), with a spread of up to $\pm 50$ samples ($\pm 150\s$).
We note that the mathematical inflection point of the tanh function
$\mathrm{pol}(t) = \tanh((t-t_\mathrm{cross})/(\delta/3))$ is at
$t_\mathrm{cross}$ --- the polarity center itself.
The observed $\pm 30\s$ localization uncertainty therefore does not arise from
a deterministic shift to a tanh sub-feature.
Instead, it reflects the combined effect of: (1) the finite chunk step size
(300 s between chunk starts, with the seam position quantized within each
200-sample window), (2) MDL scoring that maximizes segment-to-segment
compressibility gain rather than antisymmetry score, and (3) the forward-ordered
correlation formula discussed in Section~\ref{subsec:antipodal}, which does
not measure exact mirror antisymmetry.
The net result is a localization precision of approximately $\pm 30\s$.

For applications requiring precise sign-flip center localization, a
post-detection profile-fitting step (fitting a tanh model to the segment
around each detection) would recover sub-10-s accuracy.
The MDL gain score could serve as a quality metric to prioritize which events
warrant this refinement.

\subsection{Rotation Angle Analysis}
\label{subsec:angles}

Table~\ref{tab:angles} compares the magnetic field rotation angles computed
at two positions: at the raw detection position ($\omega^\mathrm{detect}$),
and at the matched injected crossing center ($\omega^\mathrm{inj}$, for
MASS/SMASH true positives only).

\begin{table}[t]
\centering
\caption{Magnetic field rotation angle analysis.
$\bar{\omega}$ = mean angle in degrees;
$f_\pi$ = fraction of events with $\omega > 160^\circ$;
KS $p$ = two-sample KS test $p$-value comparing MASS/SMASH (at detection
position) vs.\ PVI; ``At inj.'' columns are computed at the matched injected
crossing center for MASS/SMASH true positives only ($n = 58$).}
\label{tab:angles}
\begin{tabular}{lccccc}
\toprule
 & \multicolumn{2}{c}{At detection pos.} & & \multicolumn{2}{c}{At inj.\ crossing (MS TP)} \\
\cmidrule(lr){2-3}\cmidrule(lr){5-6}
Window & PVI $\bar{\omega}$ & MS $\bar{\omega}$ & KS $p$ &
         MS $\bar{\omega}$ & Inj.\ $\bar{\omega}$ \\
\midrule
10 s  & 114° & \phantom{00}1° & $1.7\times10^{-44}$ & 101° & 108° \\
30 s  & 130° & \phantom{00}4° & $1.1\times10^{-42}$ & 128° & 128° \\
60 s  & 132° & \phantom{0}42° & $4.1\times10^{-31}$ & 132° & 132° \\
120 s & 134° & \phantom{0}83° & $2.1\times10^{-13}$ & 134° & 133° \\
\midrule
\multicolumn{6}{l}{\small $f_\pi$ ($\omega>160^\circ$):
  PVI 3/7/7/8\%;
  MS-detect 0/0/0/2\%;
  MS-inj.\ 0/2/2/3\%
  (rows: 10/30/60/120 s)} \\
\bottomrule
\end{tabular}
\end{table}

\textbf{At detection positions, MASS/SMASH events show anomalously small rotation angles.}
At 10-s and 30-s averaging windows, the mean angle at MASS/SMASH detection
positions is near $0^\circ$.
This anomaly is a direct consequence of the $\pm 30\s$ detection offset: an
averaging window centered on the detection position (rather than the polarity
center) straddles the transition, averaging pre-transition and transition field
values together and driving the apparent rotation toward zero.
The KS statistics ($p < 10^{-13}$ at all window sizes) confirm highly
significant distributional differences between MASS/SMASH detection positions and
PVI events, but this distinction is a localization artifact, not evidence of
different physical event classes.

\textbf{At matched injected crossing positions, MASS/SMASH events are
indistinguishable from PVI events and the full injected population.}
When $\omega$ is computed at the matched injected crossing center for the 58
MASS/SMASH true positives, the mean angles are $101^\circ$ (10 s window),
$128^\circ$ (30 s), $132^\circ$ (60 s), and $134^\circ$ (120 s) ---
statistically indistinguishable from both the PVI catalog values
($114^\circ$, $130^\circ$, $132^\circ$, $134^\circ$) and the full injected
population ($108^\circ$, $128^\circ$, $132^\circ$, $133^\circ$) at 30--120 s
windows.
The MDL selection criterion therefore does not preferentially select
large-rotation events over moderate-rotation events: a crossing with a 120°
rotation at high SNR will score higher MDL gain than one with a 170° rotation
at low SNR, because the gain depends on compressibility, not rotation angle.

%% ============================================================
\section{Discussion}
\label{sec:discussion}
%% ============================================================

\subsection{Detection Characteristics of MASS/SMASH}
\label{subsec:char}

MASS/SMASH occupies a distinct operating point in the precision-recall space.
Its principal advantage over the $d|\mathbf{B}|/dt$ baseline is precision:
5 false detections versus 12 for the baseline (at 150-s tolerance).
Its principal disadvantage relative to the baseline is recall: 0.483 versus
1.000.
Compared to PVI, MASS/SMASH has slightly lower precision (0.921 vs.\ 0.989)
but provides complementary coverage: it finds 24 crossings that PVI misses.

The physical reason MASS/SMASH misses more crossings than the baseline is the
stringent MDL gain criterion (20 bits).
In strongly turbulent intervals, many current-sheet crossings are embedded in
high-variance background fluctuations that a single polynomial or AR model
cannot fit well regardless of seam placement, reducing the relative gain from
introducing the seam.
Lowering the gain threshold would increase recall at the cost of precision;
a systematic threshold calibration against labeled training data is desirable.

\subsection{The Detection Offset: Causes and Uses}
\label{subsec:offset_interp}

The $\approx \pm 30\s$ localization uncertainty arises from algorithmic
discretization (the MDL chunk step size is 300 s but the seam position within
each chunk is resolved to individual samples) and from the forward-ordered
antipodal correlation formula (Section~\ref{subsec:antipodal}).
The offset is not associated with a physically meaningful sub-feature of the
transition profile.

For the solar wind application, the $\pm 30\s$ precision is sufficient for
most survey work: at $\sim$4 events/day the typical inter-event spacing is
$\sim$6 hours (21{,}600 s), making the $\pm 30\s$ uncertainty $\approx 0.14\%$
of the typical inter-event interval.
For applications where precise localization matters --- measuring transition
width, estimating onset-to-peak delay, or correlating with another simultaneous
signal --- a post-detection profile fit constrained by the MASS/SMASH detection
position would provide sub-10-s accuracy.

\subsection{Multi-Detector Pipeline Design}
\label{subsec:comp}

A practical multi-stage pipeline exploiting the complementarity between
detectors is:
\begin{enumerate}
  \item Apply the baseline to obtain a high-recall ($\geq 95\%$) initial catalog.
  \item Apply MASS/SMASH with a moderate gain threshold (e.g., 5 bits) to
    re-score each event and flag those with strong structural evidence.
  \item Use the MDL gain score as a continuous quality metric rather than a
    binary threshold to rank events for detailed follow-up.
\end{enumerate}
In this pipeline, MASS/SMASH acts as a \emph{follow-on quality scorer} rather
than a standalone detector, converting the baseline's recall advantage into a
precision-ordered catalog.

\subsection{Limitations}
\label{subsec:limits}

\textbf{Synthetic data only.}
All quantitative results are from synthetic data calibrated to match statistical
properties of Wind/MFI observations.
Real solar wind current sheets exhibit a wider range of transition profiles,
background field orientations, plasma $\beta$ conditions, and co-rotating
structures not represented in our single-regime model.
Application to Wind, ACE, Parker Solar Probe, and Solar Orbiter data is required
before quantitative performance claims can be extended to real observations.

\textbf{Single-component detection and favorable synthetic geometry.}
MASS/SMASH processes only the $B_z$ component.
The synthetic benchmark was constructed with $\approx 96\%$ of the polarity
reversal amplitude in $B_z$ (field direction $\hat{\mathbf{b}}_0 = (0.20, 0.20,
0.96)$), making the benchmark favorable for $B_z$-based detection.
A follow-up benchmark should randomize the field orientation, testing performance
on oblique crossings where no single component dominates.
Full 3-component or magnitude-based MDL detection would improve recall for
such cases.

\textbf{Parameter calibration.}
The MDL gain threshold (20 bits), seam penalty ($\alpha = 2.0$), antipodal
threshold (0.35), and roughness threshold (0.20) are set heuristically.
A systematic grid search or Bayesian calibration against labeled training data
would provide a better-characterized precision-recall operating point and
enable quantitative comparison with other algorithms.

\textbf{Comparator strength.}
The $d|\mathbf{B}|/dt$ baseline is a deliberately simple screener.
In real data with a higher false discovery rate, comparison with PVI and a
vector-gradient-based baseline would provide a more demanding test of
MASS/SMASH precision.

%% ============================================================
\section{Broader Applicability}
\label{sec:applications}
%% ============================================================

The sign-flip change-point problem --- detecting a transition from a positive
steady state to an approximately equal-magnitude negative state --- appears
across many scientific and engineering domains.
We describe four additional application contexts where the MASS/SMASH framework
could be applied directly or with minor modification.

\subsection{Magnetospheric Current Sheets}
\label{subsec:magneto}

The MASS/SMASH approach transfers directly to current sheet detection in Earth's
magnetosphere.
During substorm activity, the plasma sheet in the magnetospheric tail undergoes
current sheet flapping: the sheet oscillates up and down, crossing the spacecraft
location multiple times in rapid succession and producing $B_z$ polarity
reversals at the spacecraft \citep{Chasapis2015,Retino2007}.
MMS (Magnetospheric Multiscale) and Cluster data at 25-ms to 100-ms cadence
offer the same sign-flip structure as solar wind data, but at kinetic spatial
scales and with steeper spectral slopes.
The MASS/SMASH parameters (window sizes, step sizes, antipodal threshold) would
require recalibration to the shorter correlation times and higher turbulence
amplitudes characteristic of magnetotail plasma.

\subsection{EEG and Neural Signals}
\label{subsec:eeg}

Electroencephalography signals contain polarity-reversal events in several
clinically important contexts.
Epileptic seizure transitions between ictal and post-ictal states can produce
slow-wave complexes that change sign at the transition; detection of these
sign-flip events is a component of automated seizure classification \citep{Shoeb2004}.
Phase inversions induced by bipolar electrode referencing produce artificial sign
flips in individual channel time series when a coherent source lies at or near the
reference electrode.
Detecting these inversions is a preprocessing step in source localization
pipelines.
The antipodal correlation score would provide a principled, noise-tolerant
filter for these events, since EEG is dominated by broadband $1/f$-type noise
with amplitudes comparable to the signals of interest --- the same SNR regime
as the solar wind benchmark.

\subsection{Climate Regime Shifts}
\label{subsec:climate}

Major climate modes undergo polarity reversals on interannual to multidecadal
timescales.
The El Niño--Southern Oscillation (ENSO) index (e.g., Niño-3.4 SST anomaly)
transitions between positive (El Niño) and negative (La Niña) phases with
transitions embedded in interannual variability \citep{Trenberth1990}.
The Pacific Decadal Oscillation (PDO) and Atlantic Multidecadal Oscillation (AMO)
exhibit lower-frequency sign flips on decadal timescales.
In these applications, the series is short ($N \sim 10^2$--$10^3$ monthly values),
so the chunked inference procedure would use smaller windows, and the MDL gain
threshold would require recalibration.
The antipodal correlation score provides a structurally motivated alternative
to the regression-based breakpoint tests currently used in climate regime shift
detection \citep{Killick2012}.

\subsection{AC Power Systems Fault Detection}
\label{subsec:power}

Power system faults --- line-to-line short circuits, inverter phase failures,
and neutral-to-ground faults --- produce characteristic sign-flip events in
current and voltage waveforms at line frequency (50/60 Hz).
The faulted phase undergoes a partial or complete polarity inversion relative to
the healthy phases.
Detection must occur within one to a few cycles ($\sim$16--32 ms at 60 Hz) to
trigger protective relay action.
In this context, MASS/SMASH would be applied to high-cadence current or voltage
waveforms with windows of 1--2 cycles and a step of half a cycle.
The antipodal correlation score would detect phase inversions more directly than
impedance-based relay algorithms, potentially reducing trip delay for faults
with low impedance (clean sign flip) that are currently the hardest cases for
distance relays.
Real-time implementation would require a hardware-accelerated or FPGA version
of the antipodal correlation inner loop.

%% ============================================================
\section{Conclusions}
\label{sec:conclusions}
%% ============================================================

We have introduced MASS/SMASH, an MDL-regularized algorithm for detecting
sign-flip change-points --- polarity reversals from $+\mu_0$ to $-\mu_0$
--- in noisy univariate time series.
The algorithm combines an antipodal correlation detector (which scores positions
for antisymmetry between pre- and post-event windows), a roughness discontinuity
detector (which scores for variance structure changes), and an information-theoretic
MDL model-selection step (which accepts a proposed seam only when the
compressibility gain exceeds the $\sim \log_2 N$-bit cost of specifying the
seam location).
To our knowledge, this is the first change-point detection framework to use
an antipodal symmetry score as the primary candidate generator combined with
MDL regularization for conservative event selection.

A 30-day solar wind current sheet detection benchmark against 120 known injected
polarity reversals yields the following principal findings.

\begin{enumerate}

\item \textbf{MASS/SMASH achieves 92\% precision (FDF = 7.9\%) at 150-s
tolerance} while producing only 63 detections from 120 injected crossings,
reflecting a conservative operating point set by the 20-bit MDL gain threshold.
PVI achieves precision 98.9\% at higher recall (75\%); the simple
$d|\mathbf{B}|/dt$ baseline achieves 100\% recall at 90.9\% precision.

\item \textbf{MASS/SMASH and PVI are complementary.}
Of the 58 MASS/SMASH true-positive detections, 24 correspond to crossings not
found by PVI.
A joint catalog covers 95\% of injected crossings with $\sim$5\% combined
false discovery fraction.

\item \textbf{MASS/SMASH detections carry a systematic $\approx \pm 30\s$
localization offset} from the injected polarity center, arising from finite
MDL chunk step size and the forward-ordered antipodal correlation formula.
This offset is predictable and correctable via post-detection profile fitting;
the MDL gain score can prioritize which events warrant that refinement.

\item \textbf{When corrected for the detection offset, MASS/SMASH true-positive
events have the same rotation angle distribution as PVI events and the full
injected population.}
The previously apparent small-angle anomaly at detection positions was a
localization artifact, not evidence of different physical event classes.
The MDL gain criterion does not preferentially select large-rotation events
over moderate-rotation events among genuine polarity reversals.

\end{enumerate}

Future work will focus on: (a) validation on real Wind/MFI, Parker Solar Probe
FIELDS, and Solar Orbiter MAG data; (b) extension to full 3-component or
vector-magnitude detection; (c) post-detection profile fitting for
sub-transition-width localization; (d) systematic MDL gain threshold calibration;
(e) application of the framework to EEG, climate, and power systems domains; and
(f) development of a real-time streaming version suitable for online change-point
detection.

\section*{Acknowledgments}

The author thanks the Wind/MFI team \citep{Lepping1995} and the NASA/SPDF CDAWeb
service for public archive access used during algorithm development.
Data generation and analysis used NumPy \citep{Harris2020}, SciPy
\citep{Virtanen2020}, and Matplotlib \citep{Hunter2007}.

\section*{Data and Code Availability}

All code for MASS/SMASH, synthetic data generation, PVI catalog construction,
and benchmark analysis is available at
\url{https://github.com/macmayo1993/seam-aware-modeling}.
The benchmark reproduces fully from a single command using the included synthetic
data generator.

%% ============================================================
%% References — inline thebibliography for portability (no separate .bib file).
%% To use BibTeX instead: delete the thebibliography block and uncomment:
%%   \bibliographystyle{plainnat}
%%   \bibliography{references}

\begin{thebibliography}{99}

\bibitem[Adams and MacKay(2007)]{AdamsMacKay2007}
Adams, R.~P., and D.~J.~C.~MacKay (2007),
Bayesian online changepoint detection,
\textit{arXiv preprint}, arXiv:0710.3742.

\bibitem[Basseville and Nikiforov(1993)]{Basseville1993}
Basseville, M., and I.~V.~Nikiforov (1993),
\textit{Detection of Abrupt Changes: Theory and Application},
Prentice Hall, Englewood Cliffs, NJ.

\bibitem[Bruno and Carbone(2013)]{Bruno2013}
Bruno, R., and V.~Carbone (2013),
The solar wind as a turbulence laboratory,
\textit{Living Rev. Solar Phys.}, \textbf{10}, 2,
doi:10.12942/lrsp-2013-2.

\bibitem[Canny(1986)]{Canny1986}
Canny, J. (1986),
A computational approach to edge detection,
\textit{IEEE Trans.\ Pattern Anal.\ Mach.\ Intell.}, \textbf{8}(6), 679--698,
doi:10.1109/TPAMI.1986.4767851.

\bibitem[Chasapis et al.(2015)]{Chasapis2015}
Chasapis, A., et al. (2015),
Thin current sheets and associated electron heating in turbulent space plasma,
\textit{Astrophys.\ J.\ Lett.}, \textbf{804}, L1,
doi:10.1088/2041-8205/804/1/L1.

\bibitem[Davis et al.(2006)]{Davis2006}
Davis, R.~A., T.~C.~M.~Lee, and G.~A.~Rodriguez-Yam (2006),
Structural break estimation for nonstationary time series models,
\textit{J.\ Amer.\ Statist.\ Assoc.}, \textbf{101}(473), 223--239,
doi:10.1198/016214505000000745.

\bibitem[Fearnhead(2007)]{Fearnhead2007}
Fearnhead, P. (2007),
Exact and efficient Bayesian inference for multiple changepoint problems,
\textit{Statist.\ Comput.}, \textbf{16}(2), 203--213,
doi:10.1007/s11222-006-8450-8.

\bibitem[Gosling et al.(2005)]{Gosling2005}
Gosling, J.~T., et al. (2005),
Magnetic reconnection at the magnetopause: Stress balance and velocity
changes in the exhaust,
\textit{Geophys.\ Res.\ Lett.}, \textbf{32}, L03105,
doi:10.1029/2004GL021371.

\bibitem[Greco et al.(2008)]{Greco2008}
Greco, A., P.~Chuychai, W.~H.~Matthaeus, S.~Servidio, and P.~Dmitruk (2008),
Intermittent MHD structures and classical discontinuities,
\textit{Geophys.\ Res.\ Lett.}, \textbf{35}, L19111,
doi:10.1029/2008GL035454.

\bibitem[Greco et al.(2009)]{Greco2009}
Greco, A., W.~H.~Matthaeus, S.~Servidio, P.~Chuychai, and P.~Dmitruk (2009),
Statistical analysis of discontinuities in solar wind ACE data and
comparison with intermittent MHD turbulence,
\textit{Astrophys.\ J.\ Lett.}, \textbf{691}, L111,
doi:10.1088/0004-637X/691/2/L111.

\bibitem[Harris et al.(2020)]{Harris2020}
Harris, C.~R., et al. (2020),
Array programming with NumPy,
\textit{Nature}, \textbf{585}, 357--362,
doi:10.1038/s41586-020-2649-2.

\bibitem[Hinkley(1970)]{Hinkley1970}
Hinkley, D.~V. (1970),
Inference about the change-point in a sequence of random variables,
\textit{Biometrika}, \textbf{57}(1), 1--17,
doi:10.1093/biomet/57.1.1.

\bibitem[Hunter(2007)]{Hunter2007}
Hunter, J.~D. (2007),
Matplotlib: A 2D graphics environment,
\textit{Comput.\ Sci.\ Eng.}, \textbf{9}(3), 90--95,
doi:10.1109/MCSE.2007.55.

\bibitem[Killick et al.(2012)]{Killick2012}
Killick, R., P.~Fearnhead, and I.~A.~Eckley (2012),
Optimal detection of changepoints with a linear computational cost,
\textit{J.\ Amer.\ Statist.\ Assoc.}, \textbf{107}(500), 1590--1598,
doi:10.1080/01621459.2012.737745.

\bibitem[Lavielle(2005)]{Lavielle2005}
Lavielle, M. (2005),
Using penalized contrasts for the change-point problem,
\textit{Signal Process.}, \textbf{85}(8), 1501--1510,
doi:10.1016/j.sigpro.2005.01.012.

\bibitem[Lepping et al.(1995)]{Lepping1995}
Lepping, R.~P., et al. (1995),
The Wind magnetic field investigation,
\textit{Space Sci.\ Rev.}, \textbf{71}, 207--229,
doi:10.1007/BF00751330.

\bibitem[Matthaeus and Lamkin(1986)]{Matthaeus1986}
Matthaeus, W.~H., and S.~L.~Lamkin (1986),
Turbulent magnetic reconnection,
\textit{Phys.\ Fluids}, \textbf{29}, 2513,
doi:10.1063/1.865487.

\bibitem[Neugebauer et al.(1984)]{Neugebauer1984}
Neugebauer, M., et al. (1984),
The plasma and magnetic field signatures of magnetic holes in the solar wind
and their relation to mirror-mode structures,
\textit{J.~Geophys.\ Res.}, \textbf{89}, 5395--5408,
doi:10.1029/JA089iA07p05395.

\bibitem[Osman et al.(2011)]{Osman2011}
Osman, K.~T., W.~H.~Matthaeus, A.~Greco, and S.~Servidio (2011),
Evidence for inhomogeneous heating in the solar wind,
\textit{Astrophys.\ J.\ Lett.}, \textbf{727}, L11,
doi:10.1088/2041-8205/727/1/L11.

\bibitem[Osman et al.(2014)]{Osman2014}
Osman, K.~T., et al. (2014),
Magnetic reconnection and intermittent turbulence in the solar wind,
\textit{Phys.\ Rev.\ Lett.}, \textbf{112}, 215002,
doi:10.1103/PhysRevLett.112.215002.

\bibitem[Page(1954)]{Page1954}
Page, E.~S. (1954),
Continuous inspection schemes,
\textit{Biometrika}, \textbf{41}(1/2), 100--115,
doi:10.2307/2333009.

\bibitem[Perri et al.(2012)]{Perri2012}
Perri, S., et al. (2012),
Evidence of superdiffusive transport of electrons accelerated at
interplanetary shocks,
\textit{Astrophys.\ J.\ Lett.}, \textbf{750}, L2,
doi:10.1088/2041-8205/750/1/L2.

\bibitem[Phan et al.(2006)]{Phan2006}
Phan, T.~D., et al. (2006),
A magnetic reconnection X-line extending more than 390 Earth radii in the
solar wind,
\textit{Nature}, \textbf{439}, 175--178,
doi:10.1038/nature04393.

\bibitem[Retinò et al.(2007)]{Retino2007}
Retinò, A., et al. (2007),
In situ evidence of magnetic reconnection in turbulent plasma,
\textit{Nature Phys.}, \textbf{3}, 236--238,
doi:10.1038/nphys574.

\bibitem[Rissanen(1978)]{Rissanen1978}
Rissanen, J. (1978),
Modeling by shortest data description,
\textit{Automatica}, \textbf{14}, 465--471,
doi:10.1016/0005-1098(78)90005-5.

\bibitem[Schwarz(1978)]{Schwarz1978}
Schwarz, G.~E. (1978),
Estimating the dimension of a model,
\textit{Ann.\ Statist.}, \textbf{6}(2), 461--464,
doi:10.1214/aos/1176344136.

\bibitem[Servidio et al.(2009)]{Servidio2009}
Servidio, S., W.~H.~Matthaeus, M.~A.~Shay, P.~A.~Cassak, and P.~Dmitruk
(2009),
Magnetic reconnection in two-dimensional magnetohydrodynamic turbulence,
\textit{Phys.\ Rev.\ Lett.}, \textbf{102}, 115003,
doi:10.1103/PhysRevLett.102.115003.

\bibitem[Shoeb and Clifford(2004)]{Shoeb2004}
Shoeb, A., and G.~Clifford (2004),
Application of machine learning to epileptic seizure detection,
in \textit{Proc.\ 27th Int.\ Conf.\ Mach.\ Learn.\ (ICML)}, workshop paper.

\bibitem[Trenberth(1990)]{Trenberth1990}
Trenberth, K.~E. (1990),
Recent observed interdecadal climate changes in the Northern Hemisphere,
\textit{Bull.\ Amer.\ Meteor.\ Soc.}, \textbf{71}(7), 988--993,
doi:10.1175/1520-0477(1990)071<0988:ROICCI>2.0.CO;2.

\bibitem[Truong et al.(2020)]{Truong2020}
Truong, C., L.~Oudre, and N.~Vayatis (2020),
Selective review of offline change point detection methods,
\textit{Signal Process.}, \textbf{167}, 107299,
doi:10.1016/j.sigpro.2019.107299.

\bibitem[Vasquez et al.(2007)]{Vasquez2007}
Vasquez, B.~J., C.~S.~Abramenko, D.~K.~Haggerty, and C.~W.~Smith (2007),
Electron-scale current sheets in the solar wind: Properties and
implications for particle acceleration,
\textit{J.~Geophys.\ Res.}, \textbf{112}, A11102,
doi:10.1029/2007JA012449.

\bibitem[Virtanen et al.(2020)]{Virtanen2020}
Virtanen, P., et al. (2020),
SciPy 1.0: Fundamental algorithms for scientific computing in Python,
\textit{Nature Methods}, \textbf{17}, 261--272,
doi:10.1038/s41592-020-0772-5.

\bibitem[Vostrikova(1981)]{Vostrikova1981}
Vostrikova, L.~Ju. (1981),
Detecting ``disorder'' in multidimensional random processes,
\textit{Soviet Math.\ Dokl.}, \textbf{24}, 55--59.

\bibitem[Wilcox and Ness(1965)]{Wilcox1965}
Wilcox, J.~M., and N.~F.~Ness (1965),
Quasi-stationary corotating structure in the interplanetary medium,
\textit{J.~Geophys.\ Res.}, \textbf{70}, 5793--5805,
doi:10.1029/JZ070i023p05793.

\end{thebibliography}

\end{document}
